\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/intro.tex
nit

Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g. a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the server model, beyond what is revelaed by the output
label.

Our goal is to build a framework that enables programmers, who are not
experts in cryptography, to easily program efficient and scalable \mpc
protocols. Since its introduction in 1980s, there has been a long
sequence of work along the same lines. To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Say Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server model, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w^{T}$ and $x$. Alice has following options.

@@

\begin{figure}
\begin{lstlisting}[language=C]
uint w[30] = input1(); uint b = input1();
uint x[30] = input2();
uint acc = 0;
for i in [0:30] { acc =  acc + (w[i] * x[i]); }
output((acc > b) ? 1 : 0)
\end{lstlisting}
\caption{\tool code for $w^Tx >b$}
\label{fig:ex-sml}
\end{figure}

>>>>

Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g. a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the server classifier, beyond what is revelaed by the output
label.

Our goal is to build a framework that enables programmers, who are not
experts in cryptography, to easily program efficient and scalable \mpc
protocols. Since its introduction in 1980s, there has been a long
sequence of work along the same lines. To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Say Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w^{T}$ and $x$. Alice has following options.

@@

\begin{figure}
\begin{lstlisting}[language=C]
uint w[30] = input1(); uint b = input1();
uint x[30] = input2();
uint acc = 0;
for i in [0:30] { acc =  acc + (w[i] * x[i]); }
output((acc > b) ? 1 : 0, 2) //only to party 2
\end{lstlisting}
\caption{\tool code for $w^Tx >b$}
\label{fig:ex-sml}
\end{figure}
